\documentclass[../dinner.tex]{subfiles}
\begin{document}
	\pagestyle{fancy}
	\fancyhf{}
	\newpage
	\section{Buckwheat bake}
	\lhead{}\chead{Serves 1}\rhead{V}
	\lfoot{Prep time: 10m}\rfoot{Cook time: 30m}
	{\Large Ingredients}
	\begin{multicols}{2}
		\begin{itemize}
			\item \(\frac{1}{2}\) red pepper
			\item \(\frac{1}{2}\) yellow pepper
			\item \(\frac{1}{4}\) red onion
			\item \(\frac{1}{2}\) garlic clove
			\item \(\frac{1}{2}\) cup buckwheat
			\item \(\frac{1}{2}\) tin black beans
			\item 2 tbsp cr\`eme fra\^iche
		\end{itemize}
		\columnbreak
		\begin{itemize}
			\item \(\frac{1}{4}\) tsp cumin
			\item \(\frac{1}{4}\) tsp smoked paprika
			\item \(\frac{1}{4}\) tsp cinnamon
			\item \(\frac{1}{4}\) tsp chilli powder
			\item 2 tbsp cheddar
			\item 1 tbsp chives
		\end{itemize}
	\end{multicols}

	{\Large Instructions}
	\begin{enumerate}
		\item Preheat oven to \SI{220}{\celsius}. Boil a kettle. Put the buckwheat in a bowl with a little stock powder. Add enough boiled water to just cover the buckwheat and cover with a tea towel.
		\item Remove core from peppers and chop into bite-sized chunks. Toss the peppers in 1tbsp olive oil, add to a casserole dish, and cook on the top shelf for 15 minutes (they should be slightly crispy on the edges).
		\item Peel and dice the onion and garlic. heat 1 tbsp olive oil in a pan, add the onion and garlic, cook for 5 minutes.
		\item Add the cumin, smoked paprika, cinnamon and chilli powder to the onions and garlic, stir together with a little salt \& pepper and cook. Drain the black beans and stir them in as well. Cook for another minute and then remove from the heat. 
		\item Once the peppers are done, remove from the oven and mix together with the buckwheat and spiced onion mix. stir in the  cr\`eme fra\^iche, test for seasoning and add salt \& pepper as needed.
		\item Add the mixture back into the casserole dish and top with grated cheese. Cook on the top shelf until the top is golden and crisp.
		\item Serve with a generous topping of  cr\`eme fra\^iche and a scattering of finely chopped chives.
	\end{enumerate}
\end{document}