\documentclass[../dinner.tex]{subfiles}
\begin{document}
	\pagestyle{fancy}
	\fancyhf{}
	\newpage
	\section{Cauliflower dahl}
	\lhead{}\chead{Serves 1}\rhead{V}
	\lfoot{Prep time: 5m}\rfoot{Cook time: 30m}
	{\Large Ingredients}
	\begin{multicols}{2}
		\begin{itemize}
			\item \(\frac{1}{2}\) small red onion
			\item \(\frac{1}{2}\) garlic clove
			\item \(\frac{1}{4}\) cup red split lentils
			\item \(\frac{1}{4}\) vegetable stock cube
			\item \(\frac{1}{2}\) tin chopped tomatoes
		\end{itemize}
		\columnbreak
		\begin{itemize}
			\item 1 handful cauliflower
			\item \(\frac{1}{2}\) handful green beans
			\item 1 tbsp tomato puree
			\item 1 tbsp curry powder
			\item 1 tbsp coriander
		\end{itemize}
	\end{multicols}

	{\Large Instructions}
	\begin{enumerate}
		\item Peel and dice onion and garlic. Chop cauliflower into bite-sized florets. 
		\item Add 1 tbsp oil to a large pot on medium heat, add onion and garic and cook for 5 minutes. Once soft, add a little salt \& pepper plus the curry powder and stir through.
		\item Stir in the tomato puree and the tinned tomatoes. Add in another pinch of salt and \(\frac{1}{4}\) tsp sugar. Add the red split lentils, 100ml water, and the quarter stock cube.
		\item Bring to a gentle bubble, add a lid, cook for 5 minutes.
		\item Remove the lid, add the cauliflower, replace the lid. Cook for another 15 minutes.
		\item Remove the lid, add the green beans, cook for another 5 minutes without the lid. If it's drying out add a little water. Roughly chop the coriander.
		\item Taste for seasoning, add more salt and pepper if required, and then serve topped with the coriander.
	\end{enumerate}
\end{document}