\documentclass[../dinner.tex]{subfiles}
\begin{document}
	\pagestyle{fancy}
	\fancyhf{}
	\newpage
	\section{Croquetas with romesco sauce}
	\lhead{}\chead{Serves 1}\rhead{V}
	\lfoot{Prep time: 15m}\rfoot{Cook time: 25m}
	{\Large Ingredients}
	\begin{multicols}{2}
		\begin{itemize}
			\item 1 potato
			\item \(\frac{1}{2}\) small pot sour cream
			\item Breadcrumbs
			\item A little cheddar
			\item 1 tsbp chives
			\item A few leaves of lettuce
		\end{itemize}
		\columnbreak
		\begin{itemize}
			\item 1 tomato
			\item 1 sprig rosemary
			\item 1 tsp smoked paprika
			\item 1 tsp chilli powder
			\item 1\(\frac{1}{2}\) tbsp ground almond
			\item 1 garlic clove
		\end{itemize}
	\end{multicols}
	
	{\Large Instructions}
	\begin{enumerate}
		\item Preheat oven to \SI{220}{\celsius}. Boil a large pot of lightly salted water. Peel the potato and chop into 1cm cubes. Boil for 10-15 minutes until cooked. Drain into a bowl, grate in the cheddar, and add the chives and a pinch of salt. Mash.
		\item Finely chop the tomatoes. Peel and finely dice the garlic. 
		\item Put the sour cream in one bowl and the breadcrumbs in another. Once the mash is cool enough to work with, roll them into 6 log shapes, roll in the sour cream and then roll to coat them in the breadcrumbs.
		\item Lay on baking paper on a baking tray and cook for 10 minutes on the top shelf until lightly browning.
		\item Meanwhile, add 1 tbsp olive oil to a pan and add the tomatoes. Cook for a minute or two and then add the garlic, rosemary, smoked paprika, chilli. Cook for another couple minutes and add a tbsp water and then the ground almonds. Cook until drying and then plate.
		\item Once the croquetas are cooked, serve the croquetas alongside the romesco sauce, a little sour creams, and the lettuce drizzled with oil.
	\end{enumerate}
\end{document}