\documentclass[../dinner.tex]{subfiles}
\begin{document}
	\pagestyle{fancy}
	\fancyhf{}
	\newpage
	\section{Orange-coloured tagine}
	\lhead{}\chead{Serves 1}\rhead{V}
	\lfoot{Prep time: 10m}\rfoot{Cook time: 30m}
	{\Large Ingredients}
	\begin{multicols}{2}
		\begin{itemize}
			\item \(\frac{1}{2}\) onion
			\item \(\frac{1}{2}\) sweet potato
			\item Carrot
			\item 2-3 dried apricots
			\item 1 clove garlic
			\item \(\frac{1}{2}\) cup couscous
		\end{itemize}
		\columnbreak
		\begin{itemize}
			\item 1 red chilli
			\item Ras el Hanout
			\item \(\frac{1}{2}\) vegetable stock cube
			\item \(\frac{1}{2}\) tsp muscovado sugar
			\item 1 tbsp mint
			\item 1 tbsp parsley
		\end{itemize}
	\end{multicols}

	{\Large Instructions}
	\begin{enumerate}
		\item Peel the onion, chop into two and slice one half into thin half-moons (use the other half another night). Peel and finely chop the garlic. Peel and dice half a sweet potato and a carrot. Roughly chop the apricots.
		\item Heat 1tbsp olive oil in a pan on medium heat, cook onions and garlic until soft.
		\item Boil a kettle, add couscous to a bowl with a little salt. Add enough boiled water to just cover the couscous and then cover with a tea towel.
		\item Stab the chilli a few times (more stabs = more heat). Add the ras-el-hanout to the pan and stir in. Add the chilli to the pan as well. Fry all that for another minute.
		\item Add 175ml boiling water, the half stock cube, cubed sweet potato, cubed carrot, chopped apricots, muscovado sugar. Season with a little salt \& pepper.\\
		Cover with a lid and cook for 10 minutes, then uncovered for 10-15 minutes.
		\item Finely chop the mint and parsley. Once the tagine is nearly done, uncover the couscous and add the mint and parsley to it. Stir in and fluff the couscous up using a fork.
		\item Serve the tagine over a bed of couscous.
	\end{enumerate}
\end{document}