\documentclass[../dinner.tex]{subfiles}
\begin{document}
	\pagestyle{fancy}
	\fancyhf{}
	\newpage
	\section{Pepper pasta}
	\lhead{}\chead{Serves 1}\rhead{V}
	\lfoot{Prep time: 5m}\rfoot{Cook time: 10m}
	{\Large Ingredients}
	\begin{multicols}{2}
		\begin{itemize}
			\item \(\frac{1}{2}\) onion
			\item 1 clove garlic
			\item 1 bell pepper
			\item \(\frac{1}{2}\) tin chopped tomatoes
		\end{itemize}
		\columnbreak
		\begin{itemize}
			\item 1tsp smoked paprika
			\item 2 nests tagliatelle
			\item a little cheese
			\item a few leaves of basil
		\end{itemize}
	\end{multicols}

	{\Large Instructions}
	\begin{enumerate}
		\item Peel an onion, chop into two, dice one half (use the other half another night). peel and finely chop the garlic. Remove the core from the bell pepper and dice.
		\item Heat 1tbsp olive oil in a pan on medium heat, cook pepper, onions and garlic until soft. Bring a large pot of lightly salted water to boil.
		\item Once pepper, onions and garlic are soft, stir in a teaspoon of smoked paprika. Add the chopped tomatoes, plus \(\frac{1}{2}\) tsp sugar and \(\frac{1}{4}\) tsp salt. Add the tagliatelle to the boiling water.
		\item Roughly chop the basil, grate the cheese.
		\item Let the sauce bubble (stirring occasionally), and pasta boil, for 10 minutes. Drain the pasta and stir into the sauce. Stir in \(\frac{2}{3}\) of the basil and cheese as well. 
		\item Serve topped with the remaining basil \& cheese, plus a grind of black pepper.
	\end{enumerate}
\end{document}