\documentclass[dinner.tex]{subfiles}
\begin{document}
	\pagestyle{fancy}
	\fancyhf{}
	\newpage
	\section{Sweet potato curry}
	\lhead{}\chead{Serves 1}\rhead{V}
	\lfoot{Prep time: 5m}\rfoot{Cook time: 25m}
	{\Large Ingredients}
	\begin{multicols}{2}
		\begin{itemize}
			\item \(\frac{1}{2}\) onion
			\item \(\frac{1}{2}\) garlic clove
			\item \(\frac{1}{2}\) sweet potato		
			\item 2 tsp ginger
			\item 1 tsp chilli flakes
			\item 1 tbsp curry powder
		\end{itemize}
		\columnbreak
		\begin{itemize}
			\item \(\frac{1}{2}\) tin coconut milk
			\item 75g brown rice
			\item half handful green beans
			\item 1 tbsp cashew nuts
			\item 1 tbsp desiccated coconut
			\item small bunch of coriander
		\end{itemize}
	\end{multicols}
	
	{\Large Instructions}
	\begin{enumerate}
		\item Peel and roughly chop the onion, peel and finely dice garlic. Peel and chop the sweet potato into 1cm cubes. Roughly chop the coriander.
		\item Boil a pot of lightly salted water. Wash the rice and add to the boiling water. Boil for 25 minutes.
		\item Heat a pan with 1 tbsp on medium heat, cook the onion until soft (4 mins), and add the garlic and ginger and stir through. Cook another minute. Add in the curry powder, sweet potatoes, flaked chilli, and a pinch of salt.
		\item Add in the coconut milk plus 100ml water. Cook under a lid for 10-15 minutes. Add the green beans and cook for 5 minutes.
		\item Toast the cashew nuts in a dry pan until browning, then the same with the desiccated coconut. They go from "just browned" to "burnt" very quickly so be careful.
		\item Once the sauce has bubbled down to a nice thick mixture stir through the cashew nuts and \(\frac{3}{4}\) of the coriander.
		\item Serve rice topped with curry topped with the toasted coconut and remaining coriander.
	\end{enumerate}
\end{document}